### 2018-01-26 ApproxComp/sec-introduction.tex

We systematically introduce approximate computation (\ie query and data approximation) for big data analytics, targeting at both efficiency and effectiveness in practice.

>>>>

We systematically introduce approximate computation (\ie query approximation and data approximation) for efficiency and effectiveness big data analytics in practice.
